title_uniform

### 2021-02-04 inst/examples/title_uniform.Rmd
changes

---
title: "title_uniform"
output: md_document
---
* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$title_uniform))`
 * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/title_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$title_uniform))` / `r nrow(df)` (`r round(100*mean(!is.na(df$title_uniform)), 1)`%)
 * Original documents with missing (NA) titles `r sum(is.na(df$title_uniform))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$title_uniform)), 1)`%)

>>>>

---
title: "title_uniform"
output: md_document
---
* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$title_uniform))`
 * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/title_uniform_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$title_uniform))` / `r nrow(df)` (`r round(100*mean(!is.na(df$title_uniform)), 1)`%)
 * Original documents with missing (NA) titles `r sum(is.na(df$title_uniform))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$title_uniform)), 1)`%)
